### 2021-04-30 yfcc100m/paper/vldb2021/submision/review_response/reviews_response.tex

Fixed in final version.

\bigskip

\newpage
\section{Reviewer \#4}

\bigskip
\textbf{
D1. The proposed solution seems to use the functionalities of the existing systems as it is. Authors should provide more original ideas or more innovative designs. For example, providing optimizations that specifically target visual data or query patterns associated could have been more meaningful to the research communities and convince users to replace their customized solution to VDMS.
}\bigskip

We partially address this in D3 and also elaborated more on the benefits of using VDMS over relational databases in Section 3.1.

\bigskip
\textbf{
D2. Both baselines are similar in architecture, and the evaluation has not effectively highlighted the performance gain of other design choices authors made in VDMS, except that the VDMS server process both metadata operation and image operation within only one round of communication with clients. For example, benchmarking systems can be built to test in isolation the improvement on metadata handling.
}\bigskip

Thank you for the input. To demonstrate the benefits of VDMS more clearly, we have added Figure 10 which compares queries with and without the resize operation.  Without the resize operation, the evaluation demonstrates the improvement on metadata handling better.

\bigskip
\textbf{
D3. The paper should detail the types of queries, and image preprocessing it supports, as this being “one of the most differentiating aspects” as mentioned by them. And for the selection of operations supported, authors need to argue for their decision in the application contexts.
}\bigskip

Thank you for this recommendation.  We have provided additional details on which operations we support and our decision for chosing the operations in section 3.

\bigskip
\textbf{
D4. Data scientists commonly perform data exploration on raw data and interactively curate their datasets for downstream tasks like model training. VDMS could design new mechanisms to support interactive analysis, which would be beneficial.
}\bigskip

Interactive analysis is out of scope for this paper but this can easily be done using the current implementation of VDMS.  To support interactive analysis, a new API/frontend could be implemented on top of VDMS as a webservice without adding any additional abstractions. An example of such frontend can be found <insert URL>.

\bigskip
\textbf{
D5. In terms of scalability, the paper only shows that VDMS can handle large datasets, yet it is not known how VDMS can scale horizontally with more computation resources. For more complex logic of image preprocessing, VDMS will suffer from its single server capacity.
}\bigskip

Thanks for this comment, we have added a "Future Work" section where the need for this capability in a distributed version of VDMS.

@@

\newpage
\section{Reviewer \#5}

\bigskip
\textbf{
D1: VDMS is a valuable contribution to Database systems where it takes
some first important steps to handle visual data as a first-class citizen
instead of considering it a blob of information. However, the description
of VDMS is rather short (only 4 pages), and some critical technical
details are missing. In particular, what are the technical challenges
for supporting ACID properties using the graph model abstraction? Are
the solutions analogous to RDBMS’s? Does VDMS also support crash
recovery like an RDBMS? What are the key challenges for implementing
the new visual object computations?
}\bigskip

Thank you for the comment.  In Section 3.2, we have expanded on the crash recovery of PMGD in comparison to other graph databases.

\bigskip
\textbf{
D2: The coverage of persistent memory is underwhelming because persistent memory is never used in the experiments. What is the key advantage of using persistent memory and how is it more suitable for visual data? Why not add experiments comparing VDMS with and without using PMGD?
}\bigskip

Due to page limitations and the use of SSDs instead of persistent memory in the evaluation, we did not elaborate on advantages of PMGD and related experiments.

\bigskip
\textbf{
D3: The experiments section seems unnecessarily long, yet missing some important details. All the experiments are performed on images and do not handle videos or feature values at all. For example, video operations may include interval operations or video clip retrieval. Some parts seem redundant, e.g., the description of Figure 9 seems near-identical to that of Figure 8.
}\bigskip

The paper is focused on an image search application so we did not include any experiments on videos or feature vectors. We have experiments that we can provide in appendix but due to page limitations, it did not fit the scope of this paper.

Figure 8 and 9 are quite similar but provide the performance difference with different numer of concurrent clients. We have removed figure 9 and replaced with a figure demonstrating the difference between queries with and without the resize operation.

\bigskip
\textbf{
D4: Fixed all typos
Page 1: “need for multiple system” -> “need for multiple systems”
Page 5: “desing specifically” -> “designed specifically”
Page 7: “images, taglist, and taglist” -> “images, taglist, and autotags”
Page 10, Figure 6: “10M database).” -> “10M database”
}\bigskip

All typos are fixed in the final version.

### 2021-05-03 yfcc100m/paper/vldb2021/eval.tex
Add description for resize different, remove figure 9 (16th analysis)

\begin{figure}[ht]
% WAS: begin{figure*}[ht]; textwidth
\includegraphics[width=\columnwidth]{figures/plot_th_56_mosaic_results_throughput}
\caption{Throughput Analysis using all queries from our use-case
described in the Experimental Setup Section.
We show queries in different figures for readability reasons.
The experiments show the performance of all systems (VDMS and the two baselines) as the
database size increases.
These queries were run using 56 simultaneous clients,
and averaged out of 10 runs.}
\label{fig:q_throughput_56}
\end{figure}

@@

Figure~\ref{fig:q_throughput_16} shows the measured throughput,
as images per second, delivered by each system for all queries and databases.
In comparison to figure~\ref{fig:q_throughput_56},
when using fewer concurrent clients (16),
the throughput for VDMS for queries \textit{q4}, \textit{q5}, and \textit{q6}
improved by a large margin for the 50M and 100M databases.
In the case of \textit{q4} and \textit{q6},
the throughput for 50M (and 100M for \textit{q4})
increase by a large margin which outperforms both baselines while in
Figure~\ref{fig:q_throughput_56} \textit{postgresql} slightly performed better than VDMS.
In the case of \textit{q5}, all systems perform a little differently for databases
larger than 5M.
The gaps between the throughput of each system narrows at 10M.
At a database size of 50M, the performance of the baselines drastically drop
while the throughput of VDMS has a large improvement in comparison.

>>>>

% \begin{figure}[ht]
% % WAS: begin{figure*}[ht]; textwidth
% \includegraphics[width=\columnwidth]{figures/plot_th_56_mosaic_results_throughput}
% \caption{Throughput Analysis using all queries from our use-case
% described in the Experimental Setup Section.
% We show queries in different figures for readability reasons.
% The experiments show the performance of all systems (VDMS and the two baselines) as the
% database size increases.
% These queries were run using 56 simultaneous clients,
% and averaged out of 10 runs.}
% \label{fig:q_throughput_56}
% \end{figure}

@@

% Figure~\ref{fig:q_throughput_16} shows the measured throughput,
% as images per second, delivered by each system for all queries and databases.
% In comparison to figure~\ref{fig:q_throughput_56},
% when using fewer concurrent clients (16),
% the throughput for VDMS for queries \textit{q4}, \textit{q5}, and \textit{q6}
% improved by a large margin for the 50M and 100M databases.
% In the case of \textit{q4} and \textit{q6},
% the throughput for 50M (and 100M for \textit{q4})
% increase by a large margin which outperforms both baselines while in
% Figure~\ref{fig:q_throughput_56} \textit{postgresql} slightly performed better than VDMS.
% In the case of \textit{q5}, all systems perform a little differently for databases
% larger than 5M.
% The gaps between the throughput of each system narrows at 10M.
% At a database size of 50M, the performance of the baselines drastically drop
% while the throughput of VDMS has a large improvement in comparison.

We designed VDMS with the idea in mind that pre-processing operations will be
commonly performed, as visual data is generally pre-processed before analytics
computation are performed on them.
Figure \ref{fig:q_throughput_56_resize} shows how the query throughput varies
when a pre-processing operations is applied (in this case, a resize operation).
The first thing to notice is that a resize operation is a significant part of
the overall operation (retrieval + preprocessing).
Doing a resize operation as part of the retrieval process
brings the throughput orders of magnitude down.
This is the case for both VDMS and the baseline.
Nonetheless, VDMS is orders of magnitude faster when retrieving images
both with and without resize operations.
An important thing to notice is that, even if a resized image is smaller,
and thus transfered faster between the server and the client,
transferring the image as is (without resize) is faster in this case.
This is a characteristic of the dataset, which has relatively small images
(the average image is about 150KB in size).
We have seen on other applications and datasets with higher resolution images
that transferring resized (or cropped) images is significantly faster than
transferring images as they are stored.
An interesting aspect to notice is that, when removing the resize operations,
differences between the 2 baseline systems become more noticeable.
For instance, for an image retrieval based on a single tag, we see how
\textit{postgresql} outperforms \textit{mysql}, but when adding geo-location
filtering, we see \textit{mysql} showing a small advantage.
When the resize operations is performed, both baselines do very similar
on 1tag based queries, and orders of magnitude worst than VDMS.
Note that in the baseline systems, the resize happens on the client side,
rather than on the server side.
This is the common case in most analytics applications, where pre-processing
operations happen on the client side (or when the analytics computation happens),
rather than near where the data is located, as it is the case with VDMS.
We kept both the server and client systems the same to avoid the computation
capabilities difference complicating our understanding of the results.
